Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-01 paper.tex
Add to intro

@@

>>>>

Computational fluid dynamics (CFD) presents an attractive method for simulating
cross-flow turbines since it only requires turbulence modeling, i.e., the
machine is described from first principles. However, CFD can be computationally
expensive when done in three dimensions, which may be necessary in some cases.
There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results.

@@

Note that studies in the literature generally focus on predicting the turbine
loading and the local blade flow rather than the turbine wake. In contrast, we
seek to model the near-wake flow.
